### 2023-03-12 main/chapter_2ljets.tex
explain why low-isr is included

\subsubsection{Low-ISR}
\label{sec:2ljets_low_isr}
The Low regions presented in Section~\ref{sec:2ljets_low} resulted from a
hasty redesign shortly before unblinding.
Before that redesign, a multi-jet signal region SR-Low-ISR was included,
with associated validation and control regions
that required $\njet \geq 3$ and offered some meagre extra sensitivity.
Here, `ISR' stands for Initial-State Radiation, following the naming
of previous \atlas\ searches including partial Run~2 $2\ell$/$3\ell$
search which we are updating~\cite{atlas_23l_SUSY_2016_24} in the
$\twoljets$-electroweak search.

@@

A complicated likelihood model was constructed, which normalized \diboson,
$\zjets$ and $\ttbar$ backgrounds to the combination of CR-Low-ISR,
CR-Low-ISR-Z, CR-Low-ISR-DF.
After this fit, the validation region VR-Low-ISR had a high background yield
of $56.7 \pm 4.4$ for $47$ data, which is only a $1$-sigma deficit.

>>>>

\subsubsection{Low-ISR}
\label{sec:2ljets_low_isr}
The Low regions presented in Section~\ref{sec:2ljets_low} resulted from a
hasty redesign shortly before unblinding.
Before that redesign, a multi-jet signal region SR-Low-ISR was included,
with associated validation and control regions
that required $\njet \geq 3$ and offered some meagre extra sensitivity.
Here, `ISR' stands for Initial-State Radiation, following the naming
of previous \atlas\ searches including the partial Run~2 $2\ell$/$3\ell$
search, which we are updating~\cite{atlas_23l_SUSY_2016_24} in the
$\twoljets$-electroweak search.
Although these Low-ISR regions were removed from the analysis and we never
inspected the data in SR-Low-ISR (never unblinded), I include them here because
they reveal some interesting context to the surviving analysis design.
Specifically, prototype validation regions for Low-ISR designs revealed some
bad modelling by our Standard Model background samples in phase space that is
close to SR-Low, which is a region where we observe significant data deficits.
Secondly, these regions were an impactful part of the analysis design process
and led to the final design of SR-Low;
describing my experiences with them therefore reveals more about the true
design process.

@@

A complicated \heplikelihood\ model was constructed, which normalized \diboson,
$\zjets$ and $\ttbar$ backgrounds to the combination of CR-Low-ISR,
CR-Low-ISR-Z, CR-Low-ISR-DF.
After this fit, the validation region VR-Low-ISR had a high background yield
of $56.7 \pm 4.4$ for $47$ data, which is only a $1$-sigma deficit.
